### 2020-08-24 0_abstract.tex
Update abstract.

% 150 words

\begin{abstract}
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench dramatically lowers the barrier to benchmarking and comparing multiple programming systems by making
the implementation for a given system orthogonal to the benchmarks
themselves: every benchmark constructed with Task Bench
runs on every Task Bench implementation. Furthermore,
Task Bench's parameterization enables a wide variety of benchmark
scenarios that distill the key characteristics of larger applications.

We conduct a comprehensive study with
15 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We introduce a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each
system. Running at scale, 100~\textmu{}s is the
smallest granularity that any system can reliably
support with current technologies. We also study each system's
scalability, ability to hide communication and mitigate load
imbalance.
\end{abstract}

>>>>

% 149 words

\begin{abstract}
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance of distributed programming systems under a
variety of application scenarios. Task Bench dramatically lowers the
barrier to benchmarking and comparing multiple programming systems by
making the implementation for a given system orthogonal to the
benchmarks themselves: every benchmark constructed with Task Bench
runs on every Task Bench implementation. Furthermore, Task Bench's
parameterization enables a wide variety of benchmark scenarios that
distill the key characteristics of larger applications.

To assess the effectiveness and overheads of the tested systems, we
introduce a novel metric, \emph{minimum effective task granularity}
(METG). We conduct a comprehensive study with 15 programming systems
on up to 256 Haswell nodes of the Cori supercomputer. Running at
scale, 100\textmu{}s-long tasks are the finest granularity that any
system runs efficiently with current technologies. We also study each
system's scalability, ability to hide communication and mitigate load
imbalance.
\end{abstract}

### 2020-08-24 8_case_study.tex

Early Task Bench results for Dask revealed that the cost of scheduling
a task was $\mathcal{O}(N)$ where $N$ is the number of tasks in a task
graph, causing overall cost for a task graph with $N$ nodes to be
$\mathcal{O}(N^2)$. This issue was reported to and confirmed by the
Dask developers; the bug is suspected to be in optimizations performed
on the task graph by Dask. As a work around, our results in the paper use a
lower-level interface which does not suffer from this asymptotic
slowdown.

TensorFlow performs optimizations on task graphs prior to execution,
including a constant folding pass. The Task Bench implementation uses
aggressive loop unrolling to minimize overheads, resulting in the task
graph being marked as constant. Because TensorFlow optimizations are
performed on a single core, this resulted in sequential execution of
the entire graph, and Task Bench experiments timed out. As a
workaround, additional inputs can be fed to nodes in the graph to make
them non-constant, forcing them to be executed by TensorFlow's normal
scheduler. Though this was exacerbated by Task Bench's approach to
unrolling loops, it affects any task graph with constants that are
expensive to compute where the users may wish to perform
constant-folding in parallel.

>>>>

Early Task Bench results for Dask revealed that the cost of scheduling
a task was $\mathcal{O}(N)$ where $N$ is the number of tasks in a task
graph, causing overall cost for a task graph with $N$ nodes to be
$\mathcal{O}(N^2)$. This issue was reported to and confirmed by the
Dask developers; the bug is suspected to be in optimizations performed
on the task graph by Dask. As a workaround, our results in the paper use a
lower-level interface which does not suffer from this asymptotic
slowdown.

TensorFlow performs optimizations on task graphs prior to execution,
including a constant folding pass. The Task Bench implementation uses
aggressive loop unrolling to minimize overheads, resulting in the task
graph being marked as constant. Because TensorFlow optimizations are
performed on a single core, this resulted in sequential execution of
the entire graph, and Task Bench experiments timed out. As a
workaround, additional inputs are fed to nodes in the graph to make
them non-constant, forcing them to be executed by TensorFlow's parallel
scheduler. Though this was exacerbated by Task Bench's approach to
unrolling loops, it affects any task graph with constants that are
expensive to compute where the users may wish to perform
constant-folding in parallel.
